(Tentative) Calculating Green Function

### 2016-08-31 Green function/green-f.tex
Chapter one of the new green-func

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{book}

@@

\maketitle
\abstract{
    This is a note for reading the paper \cite{1}, and for understanding
    the code produced from that file.
}
\tableofcontents

\begin{thebibliography}{1}
    \bibitem{book} Complex Geometry
\end{thebibliography}
\chapter{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

>>>>

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

@@

\maketitle
\abstract{
    This is a note for reading the paper \cite{dissertation}, and for understanding
    the code produced from that file.
}
\tableofcontents

\section{Chapter 1 - Introductions}
\label{sec:Chapter 1 - Introductions}
This chapter is really a nice introduction to the current fields of mesoscopic physics.
The writing is clear and it traces the develpment of this field. It gives me a lucid
and holistic historical account of both the important discoveries and motives behind
them. I should find those marked regions on pdf inside this part very useful.

\begin{thebibliography}{1}
    \bibitem{dissertation} 
        \href{https://sundoc.bibliothek.uni-halle.de/diss-online/07/07H039/prom.pdf}{Electronic Transport in Mesoscopic Systems}, 
        by von Georgo Metalidis. (Link found via Google)
\end{thebibliography}
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}
